---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cpdb

<!-- badges: start -->
<!-- badges: end -->

## Description
This R package allows the user to get the intramolecular contacts of a specific residue from a solved PDB protein structure. Its use is intended to researchers in genetic mutations.

## Installation
Install the package

```{r, eval=FALSE, tidy = TRUE, size="tiny"}
library(devtools)
devtools::install_github("karlapenag/cpdb", build_vignettes = TRUE)
```

```{r setup}
library(cpdb)
```


## `get_contacts()` function

This function has four arguments,`pdb`, `chain`, `res` and `a`.

`pdb` and `chain` have to be `strings`. The default for `chain` is `"A"`.
`res` is the position number of the residue in the protein sequence.
`a` is the distance in angstroms. Default = 8. 

returns a `text` with the residue contacts.

## `plot_closest()` function

This function has the same four arguments,`pdb`, `chain`, `res` and `a`.

`pdb` and `chain` have to be `strings`. The default for `chain` is `"A"`.
`res` is the position number of the residue in the protein sequence.
`a` is the distance in angstroms. Default = `8`. 

returns a ´plot´ of the closest residues to the target residue.

### Example
```{r}
get_contacts("4q21", "A", 15, 6)
```

```{r}
plot_closest("4q21", "A", 15, 8)
```
